Software Citation Principles

### 2016-03-02 sc-principles/software-citation-principles.tex
fixes to affils

James Howison, UTexas

Lorraine Hwang, UC Davis

@@

Daniel S. Katz, U Chicago \& Argonne Natl Lab (co-chair)

@@

Brian Matthews, Science and Technology Facilites Council

@@

Soren Scott , Independent Researcher

@@

Ilian Todorov, STFC

>>>>

James Howison, University of Texas

Lorraine Hwang, University of California,  Davis

@@

Daniel S. Katz, University of Chicago \& Argonne National Laboratory (co-chair)

@@

Brian Matthews, Science and Technology Facilities Council

@@

Soren Scott, Independent Researcher

@@

Ilian Todorov, Science and Technology Facilities Council
